%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{xcolor}
\usepackage{fontawesome5}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
\usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\newcommand{\linkicon}{
  \color{gray}{\footnotesize\raisebox{1pt}{\faIcon{external-link-alt}}}
}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}


%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Gaurav Sharma} \\ \vspace{4pt}
      \href{tel:+91-8054533256}{{\color{gray}{\faPhone}} +91 80545 33256} \quad
  \href{mailto:gauravsharma01042000@gmail.com}{{\color{gray}{\faEnvelope}} gauravsharma01042000@gmail.com} \quad 
  \href{https://www.linkedin.com/in/gaurav-sharma-6b457a1ab/}{{\color{gray}{\faLinkedin}} gaurav-sharma-6b457a1ab} \quad
  \href{https://github.com/Gekko12}{{\color{gray}{\faGithub}} Gekko12} \quad
  
  % \href{https://github.com/}{{\color{gray}{\faLink}} starportfolio.com} 
\end{center}


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Tata Consultancy Services}{Aug 2022 -- Present}
      {Data Engineer (Kenvue Inc.  as Client) $|$ \emph{Python, SQL, Treasure Data CDP, SFMC API, Git}}{Bengaluru, India}
      \resumeItemListStart
        \resumeItem{Designed and implemented \textbf{ETL pipelines} and data orchestration workflows for efficient data extraction and integration.}
        \resumeItem{Developed and automated end-to-end \textbf{CCPA} compliance workflows, \textbf{reducing manual effort} and enhancing regulatory adherence across digital platforms.}
        \resumeItem{Implemented automated pipelines to \textbf{migrate and integrate} large-scale consumer datasets from \textbf{Snowflake into CDP} environments, optimizing data quality and enabling real-time marketing activation.}
        \resumeItem{Integrating \textbf{Treasure Data's Customer Data Platform (CDP)} with The \textbf{Trade Desk DSP} to enable advanced audience targeting across \textbf{digital advertising} channels.}
      \resumeItemListEnd     
% -----------Multiple Positions Heading-----------
    \resumeSubSubheading
    {Python Developer (Johnson \& Johnson  as Client) $|$ \emph{Python, Django, REST APIs, Git}}{Bengaluru, India}
    \resumeItemListStart
       \resumeItem{Developed scalable backend logic to support dynamic UI-based functionality, ensuring seamless user interaction.}
       \resumeItem{Built \textbf{modular components to integrate APIs, databases, and file storage systems} using Python, enhancing system connectivity and performance.}
       \resumeItem{Designed and implemented an \textbf{ETL framework} leveraging \textbf{object-oriented programming (OOPs)} and \textbf{software design patterns} to streamline data processing.}
       \resumeItem{Built and deployed \textbf{RESTful APIs using Django}, enabling smooth communication between frontend and backend services.}
    \resumeItemListEnd

    \resumeSubheading
    {Persistent Systems}{Feb. 2022 -- Jul 2022}
      {Software Engineer $|$ \emph{Python, Django, REST APIs, Git}}{Bengaluru, India}
      \resumeItemListStart
        \resumeItem{Designed and developed \textbf{RESTful APIs using Django REST Framework} for scalable web applications.}
        \resumeItem{Implemented \textbf{CRUD operations}, authentication, and middleware to handle secure and efficient data processing.}
        \resumeItem{Integrated APIs with frontend clients and third-party services to enable smooth data communication.}
        \resumeItem{Followed best practices for code structure, \textbf{version control} (Git), and \textbf{API documentation} for maintainability.}
    \resumeItemListEnd

\resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Eco-Fertilization} \href{https://github.com/Gekko12/Eco-fertilization}{{\color{gray}{\faLink}}} $|$ \emph{Python, Flask, Pandas}}{Nov 2021 -- Jun 2022}
          \resumeItemListStart
            \resumeItem{Developed a \textbf{rainfall-aware fertilizer recommendation system} using a \textbf{time-series} based \textbf{Random Forest algorithm} to optimize crop nutrient delivery (N, P, K) and \textbf{minimize runoff risks}.}
            \resumeItem{ Integrated \textbf{weather forecasting} data with soil fertility analysis to provide dynamic nutrient suggestions, \textbf{enhancing crop yield potential} and environmental sustainability.}
            % \resumeItem{Built a \textbf{responsive web application} using Flask to deliver real-time N:P:K ratio predictions and 7-day weather forecasts, improving decision-making for farmers.}
            % \resumeItem{Utilized Python (Pandas, Scikit-learn, Category Encoders, Matplotlib) for data processing, model development, and visualization; deployed locally via a browser-based interface.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Ajna - The Covid Envision} \href{https://github.com/Gekko12/Ajna-The_Covid_Envision}{{\color{gray}{\faLink}}} $|$ \emph{Python, Tkinter GUI, SQLite}}{Dec 2020 -- Jan 2021}
          \resumeItemListStart
            \resumeItem{Developed a \textbf{desktop-based COVID-19 contact tracing and self-assessment application} using Python and Tkinter to track user interactions, travel history, and risk status in a college setting.}
            % \resumeItem{Implemented a local SQLite3 database to securely store user data, meet/travel history, and COVID-19 zone classifications, enabling efficient querying and daily log updates.}
            \resumeItem{Built an \textbf{interactive GUI} with Tkinter to support \textbf{user registration, login and dynamic status updates} (Green, Yellow, Red) based on contact tracing logic.}
            % \resumeItem{Integrated self-assessment feature, providing immediate risk evaluation and color-coded status based on symptoms, contact history, and location data.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd


%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, Java, SQL (Postgres)} \\
     \textbf{Frameworks}{: Django, Flask, Pandas, NumPy, Matplotlib} \\
     \textbf{Developer Tools}{: Git, VS Code, PyCharm, Treasure Data CDP, Snowflake, Amazon Web Services} \\
    }}
 \end{itemize}

%-----------CERTIFICATIONS-----------
\section{Certifications}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
    {\textbf{Microsoft Certified: Azure Fundamentals} \quad \href{https://learn.microsoft.com/en-us/users/gauravsharma-7801/credentials/33e44c5243560a03}{{\color{gray}{\faLink}}}} 

     {\textbf{AWS Certified Developer – Associate} \quad \href{https://www.credly.com/badges/fe0c1bcc-c577-4f17-b96e-46935268b3f7/linked_in_profile} {{\color{gray}{\faLink }}}} 
    
     {\textbf{SnowPro Core} \quad \href{https://achieve.snowflake.com/b121fd98-943a-4de3-b9e4-3e6e518280e1#gs.g08k0q}{{\color{gray}{\faLink}}}} 
     }}
 \end{itemize}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Atria Institute of Technology, Bengaluru}{Aug. 2018 -- Jul 2022}
      {BE, Computer Science \& Engineering}{GPA: 9.04/10.0}
    % \resumeSubheading
    %   {Kendriya Vidyalaya ASC, CBSE}{Bengaluru}
    %   {Higher Secondary Education in Science}{Apr. 2017 -- May 2018}
  \resumeSubHeadingListEnd



%-------------------------------------------
\end{document}
