\documentclass[a4paper,20pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
% \usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage[hidelinks]{hyperref}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{soul}
\setul{1.5pt}{0.4pt}



\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.55in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \hspace{6cm}\textbf{{\fontsize{20}{20}\selectfont Gaurav Sharma}}
\end{tabular*}\\
\vspace{5pt}

\hspace{2.4cm}
+91 80545 33256 \( \mid \) gauravsharma01042000@gmail.com \( \mid \)
{\href{https://www.linkedin.com/in/gaurav-sharma-6b457a1ab/}{LinkedIn  \( \mid \)}}
{\href{https://github.com/Gekko12/}{GitHub \( \mid \)}}
{\href{https://leetcode.com/u/GekkoCode/}{LeetCode  }}


%----------- EDUCATION :: START -----------------
\section{Education}
\vspace{1pt}
  \textbf{University Visvevaraya College of Engineering}\hspace{2cm}\hspace{2cm}\hspace{2mm}\hspace{2mm}\hspace{24mm}\hspace{2mm}\normalfont Aug 2022 – Jun 2026\\
  \textit{B.Tech - Computer Science And Engineering}\hspace{2cm}\hspace{2cm}\hspace{2cm}\hspace{3.6cm} \normalfont CGPA: \textbf { 9.4} \\  
  
  \vspace{3pt}
  \textbf {PM Shri Kendriya Vidyalaya – A.S.C Centre(S)}\hspace{6.7cm} \normalfont Jun 2016 – Jun 2022\\
  \textit{Bangalore, India}\hspace{9.5cm}\hspace{2.3cm} \normalfont CBSE Class 12th:\textbf { 96.6\%} \\
  \hspace{12cm}\hspace{2.4cm} \normalfont CBSE Class 10th:\textbf { 94.8\%}\\	    
\vspace{1pt}
%----------- EDUCATION :: END -----------------


%----------- SKILLS :: START -----------------
\section{Technical Skills }
\vspace{2pt}

\textbf{Languages: }\hspace{0.1cm} \normalfont Python, Java, C, HTML, CSS\\
\textbf{Databases: }\hspace{0.1cm} \normalfont MySQL, SQLite\\
\textbf{Version Control: }\hspace{0.1cm} \normalfont Git, GitHub\\
\textbf{Operating Systems: }\hspace{0.1cm} \normalfont Linux (Ubuntu), Windows\\
\textbf{Soft Skills: }\hspace{0.1cm} \normalfont Leadership, Public Speaking, Time Management, Motivated Learner\\
%-----------SKILLS :: END -----------------


%----------- AWARDS :: START -----------------
\vspace{-5pt} 
\section{Achievements}
\vspace{2pt}

\begin{enumerate}
\item {\textbf{1st} Ranked in Best Cadet Flying at All India Vayu Sainik Camp of NCC AirWing and recipient of \textbf{DG NCC Commendation Card} }
\vspace{-5pt}
\item {\textbf{2nd }Rank in Science stream (CS Branch) in K.V - A.S.C, CBSE Class 12th (2022)}
\vspace{-5pt}
\item {Ranked \textbf{3} in Flying All India \textbf{NDA} ( National Defence Academy ) Exam, and \textbf{269} ranked in overall Merit }
\vspace{-5pt}
\item {\textbf{Among top 1.5\% }out of 20 lac+ students in AISSE ( All India Secondary School Examinations), CBSE (2022)}
\vspace{-5pt}
\item {Ranked \textbf{2000} in IISER Applitude Test 2022 }
\vspace{-5pt}
\end{enumerate}
%----------- AWARDS :: END -----------------


%----------- LEADERSHIP :: START -----------------
\vspace{-7pt}
\vspace{2pt}
\section{Leadership}
\vspace{2pt}
\begin{enumerate}
\item {\textbf{NCC} ( National Cadets Corp ) C Certificate - Air Wing }
\vspace{-5pt}
\item {Represented Karnataka and Goa in All India Level Vayu Sainik Camp 2024 in Flying team 
 and Drill Contingent }
\vspace{-5pt}
\item { Best Class Competition 5.0  Class Coordinator, conducted by UVCE Graduate Association}
\vspace{-5pt}
\end{enumerate}
\vspace{-7pt}
%----------- LEADERSHIP :: END -----------------


%----------- PROJECTS :: START -----------------
\vspace{1pt} 
\section{Projects}
\vspace{2pt}
{\textbf{\ul{Full-Stack Django Web Application}}} \normalfont  \(\mid\) (Django, Python, HTML, CSS, SQLite, DRF)
\vspace{-5pt}

\begin{itemize}[itemsep=0pt]
  \item Built a feature-rich web app with messaging, comments, ratings, and a voting system.
 \item Integrated real-time messaging using Django Channels \& WebSockets.
\item Developed RESTful APIs with DRF for external integrations.
\item Implemented search, pagination, and email functionality for better user experience.
\item Deployed on AWS with security best practices.
\end{itemize}

\textbf{\ul{Hog Rider RPG (Role-Playing Game)}}\normalfont{ } \( \mid \) (Python, Pygame, Object-Oriented Programming)
\vspace{-5pt}

\begin{itemize}[itemsep=0pt]
  \item Developed a 2D endless runner game using Pygame for rendering, physics, and collision detection..
\item Designed an intuitive GUI with real-time score, health, and power-up indicators.
\item Integrated SQLite to store high scores and player progress.
  \item Applied OOP principles to modularize game components for scalability and efficient debugging.
\end{itemize}
\vspace{-5pt}
%----------- PROJECTS :: END -----------------

%----------- EXTRAS :: START -----------------
\section{Extracurricular}
\vspace{1pt}
\textbf{Organised and Volunteered in Events } 
\\
\vspace{-5pt}

\begin{itemize}[itemsep=0pt]

  \item Organised and Volunteered in Events conducted by IEEE UVCE - IMPETUS Kagada
  
\end{itemize}

\textbf{Nationals Table Tennis and Regionals Badminton}
\vspace{-5pt} 

\begin{itemize}[itemsep=0pt]
  \item Played nationals in Table Tennis, solo as well as doubles.
  \item Played regionals in Badminton.
  
\end{itemize}
%----------- EXTRAS :: END -----------------


%----------- INTERESTS :: START -----------------
\section{Interests}
\vspace{1pt}

\textbf{Sports and Running: } \normalfont Participated in various Running events\\

\textbf{Geopolitics: } \normalfont Understanding of India’s Foreign Relations and Global Affairs\\
%----------- INTERESTS :: END -----------------

  
\end{document}